%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\begin{flushright}{\slshape    
   Listen to advice and accept instruction, and in the end you will be wise.} \\ \medskip
    --- Pr. 19:20
\end{flushright}



\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}

First and foremost I would like to express sincere gratitude to my supervisor Dr Anil Anthony Bharath, for accepting me as a PhD student and for his continuous support at every stage of the PhD. I believe I am privileged as his excellence in PhD supervision went beyond than just expert technical advice. He instilled perseverance in me and showed me with his tireless effort that the hard-work and ambition are the best cure against the many insecurities that many PhD students suffer at some point during our studies.

I would also like to thank the members of the Biologically Inspired Computer Vision Group (BICV). Being surrounded by extraordinarily bright people is the richest source of motivation. In particular, I would like to thank Dr Lucas Hadjilucas for his enthusiasm and patience when passing the knowledge on many aspects of systems engineering and servers infrastructure that have been so valuable for me. Also to Dr Ioannis Alexiou, for providing many scientific contributions that helped lay the foundations for my research and for co-authoring many of our publications so far. Also to Christoforos Charalambus, for always being there in the last three years. Special thanks go to Kai Arulkumaran, with whom I share many views on how new technology and modern approaches to scientific research can have a great impact in a PhD and add incredible value to a research group. His enthusiasm  and hard-work have been a source of motivation for the late stage of my PhD. Also thanks to all the undergraduate, MSc and visiting PhD students that at some point were part of the BICV group, a source of new and fresh ideas and always willing to lend a hand with my data collection projects. Special within this group is Saad Idrees, a kind friend and a true example of professionalism, endurance and impeccable work ethic. I also take this opportunity to sincerely acknowledge Dr Riccardo Secoli for his help and guidance at the early stages of my PhD. To him I owe becoming a Linux power user and his advice helped me define many aspects of my PhD and to find the most important priorities in times of struggle.

On the personal side, I am most grateful to my parents, for teaching me the values to achieve success in life. Their integrity, hard-work and love for education have been important pillars of my PhD, adding the motivation, strength and endurance that is needed to accomplish a PhD.

I would like to thank Myriam for always being at my side. For encouraging me to pursue a PhD and always follow my dreams and ambitions, and who has given me unconditional support during these 4 wonderful years in London in which we have achieved so much. It seemed eternal, but we are almost there. Without her, this work would not have been possible.

Finally, I would like to express my gratitude to all my friends that have been supportive throughout the PhD and the writing of this thesis. Special thanks to those friends who also are (or were) PhD students once. They are the best counselling service that can be offered to a doctoral student. A continuous source of support and well-being recipes: Sergio Conde Martin, Aguila Ruiz Sola, Toni Alomar Sitges and Maxi Gandul Galiano.

My research was funded by an EPSRC DTP scholarship and an EPSRC Translation Award. The hosting of the datasets is supported by the EPSRC V\&L Net Pump Priming Grant 2013-1. 

\endgroup



